---
title: "case_study"
output: html_document
---

Load key packages
```{r}
library(p8105.datasets)
library(tidyverse)
library(leaflet)

data(nyc_airbnb)
```

## Brainstorm questions

* Pick a neighborhood / borough, investigate price
  * If we had dates, does that affect price?
* Does the type of unit affect rating / price?
* What about ZIP codes?
* What rental has the highest reviews?
* Are there any connections between price and other variables?
* What about prices over time?
  * Could we look at prices before and after the pandemic?
* How else did the pandemic affect AirBNB in NYC?
* Does the name of the rental affect the price/rating?
* What does the number of days available have to do with anything else?

Let's look at prices first
```{r}
nyc_airbnb |>
  drop_na(price) |>
  group_by(neighbourhood_group) |>
  summarize(
    mean_price = mean(price),
    min_price = min(price),
    max_price = max(price)
  )
```

What about room type in a given neighbourhood?
```{r}
nyc_airbnb |>
  drop_na(price) |>
  # filter(neighbourhood_group== "Manhattan") |>
  group_by(room_type, neighbourhood_group) |>
  summarize(
    mean_price = mean(price),
    # min_price = min(price),
    # max_price = max(price)
  ) |>
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```


```{r}
nyc_airbnb |>
  count(neighbourhood_group, room_type)
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         price < 500,
         room_type == "Entire home/apt") |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |>
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```




let's make some plots
```{r}
nyc_airbnb |>
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(room_type ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0,1000))
```

```{r}
nyc_airbnb |>
  filter(price > 9000)
```

```{r}
nyc_airbnb |>
  filter(calculated_host_listings_count > 30)
```

Keep looking at location
```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         price < 1000,
         room_type == "Entire home/apt") |>
  ggplot(aes(x = lat, y = long, color = review_scores_location)) +
  geom_point()
```

can we make a better map
```{r}
pal <-colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$review_scores_location
)

nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         room_type == "Entire home/apt") |>
  leaflet() |>
  # addTiles() |>
  addProviderTiles(providers$CartoDB.Positron) |>
  # addMarkers(~lat, ~long)
  addCircleMarkers(
    ~lat, ~long,
    color = ~pal(review_scores_location),
    radius = 2
  )
```

